Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-08 paper/paper.tex
Muck around with abstract and intro

\begin{abstract}
    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
    ``as much of the pattern as possible'' inside the target graph. In general, this is maximum
    common subgraph problem, which is much more computationally challenging in practice than
    subgraph isomorphism. We present and evaluate a new constraint-style algorithm which lies
    between these two approaches, for cases when nearly all of the pattern is present.
\end{abstract}

@@

The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case below). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem becomes computationally
infeasible at only 35 vertices when working with unlabelled graphs \citep{DBLP:conf/cp/McCreeshNPS16}. This is
largely because strong inference, based upon the degrees of vertices
\citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted. In
this work we discuss an intermediate problem, where we must map all but $k$ vertices of the pattern
graph into the target. We show that if $k$ is reasonably small (say, between 1 and 5), then weakened
forms of degree and path based filterings are still effective in pruning the search space and
providing additional constraints respectively. We then show that combining these techniques does
lead to a practical algorithm which can scale to work with the families of graphs commonly used to
benchmark subgraph isomorphism algorithms: depending upon the benchmark family, in a substantial
portion of ; in many more cases, we can at least obtain an upper bound.

>>>>

\begin{abstract}
    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
    ``as much of the pattern as possible'' inside the target graph. In general, this is maximum
    common subgraph problem, which is much more computationally challenging in practice than
    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
    vertices from the pattern can be found in the target. This allows us to develop slightly
    weakened forms of certain invariants from subgraph isomorphism, retaining most of their
    effectiveness. For small values of $k$, we can solve this problem on most of the standard problem
    instances used to benchmark subgraph isomorphism algorithms, despite these instances being much
    too large for current maximum common subgraph algorithms to handle.
\end{abstract}

@@

The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case below). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem becomes computationally
infeasible at only 35 vertices when working with unlabelled graphs
\citep{DBLP:conf/cp/McCreeshNPS16}. This is largely because strong inference, based upon the degrees
of vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted,
whilst filtering during search is vastly stronger.

In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
pattern graph into the target. We show that if $k$ is reasonably small (say, between 1 and 5), then
weakened forms of degree and path based filterings are still effective in pruning the initial search
space and in providing additional constraints respectively. We then show that combining these
techniques leads to a practical algorithm which can scale to work with the families of graphs
commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, in
a substantial portion of ??; in ?? more cases, we can at least obtain an upper bound.
